---
title: "Untitled"
author: "Kelly Hondula"
date: "2022-11-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(terra)
library(glue)
library(dplyr)
library(purrr)
library(scico)
library(sf)
```

```{r}
base_dir <- 'Y:/'
# base_dir <- '/Volumes/alab/CarbonMapper'
minerals_df <- readr::read_csv('Minerals.csv')
mixtures_df <- readr::read_csv('Mixtures.csv')
ems_df <- readr::read_csv('AllEndmembers.csv')
source('color-pals.R')
source('crop-n-drop.R')
```


```{r}
cube_path <- glue('{base_dir}/software/tetracorder-essentials/example/input/ang20200712t201415_corr_v2y1_img')
cube_id <- basename(cube_path)
orig_rast <- terra::rast(cube_path)
tet_out_dir <- glue('{base_dir}/software/tetracorder-essentials/example/output/try1')
plots_dir <- glue('{base_dir}/Scratch/kellyh/tetplots/AluniteHill')
```

```{r}
orig_ext <- terra::ext(orig_rast)
orig_crs <- terra::crs(orig_rast)

zoom_size <- 500

# 400
# 1280
#  ???
# my_x <- terra::xFromCol(orig_rast, 300)
# my_y <- terra::yFromRow(orig_rast, 1630)
# my_ext <- terra::ext(c(my_x-zoom_size, my_x+zoom_size, my_y-zoom_size, my_y+zoom_size))

# Alunite Hill
my_x <- terra::xFromCol(orig_rast, 392)
my_y <- terra::yFromRow(orig_rast, 2700)
my_ext <- terra::ext(c(my_x-zoom_size, my_x+zoom_size, my_y-zoom_size, my_y+zoom_size))

# MIDDLE OF IMAGE
# mid_x <- as.numeric(orig_ext[1] + (orig_ext[2]-orig_ext[1])/2)
# mid_y <- as.numeric(orig_ext[3] + (orig_ext[4]-orig_ext[3])/2)
# my_ext <- terra::ext(c(mid_x-zoom_size, mid_x+zoom_size, mid_y-zoom_size, mid_y+zoom_size))
```

# RGB

```{r}
my_aoi_sf <- my_ext %>% st_bbox() %>% st_as_sfc() %>% st_as_sf()

make_rgb <- function(){
  terra::plotRGB(orig_rast, r = 54, g = 36, b = 20, 
               scale = 10000,
               stretch = 'lin', 
               ext = my_ext, colNA = 'black')}

# pdf(file = glue('{plots_dir}/rgb.pdf'))
make_rgb_box <- function(){
  terra::plotRGB(orig_rast, r = 54, g = 36, b = 20,
               scale = 10000,
               stretch = 'lin',
               # ext = my_ext, 
               colNA = 'white')
  plot(my_aoi_sf, add = TRUE, border = 'red', lwd = 2)
  
}



# dev.off()

# png(file = glue('{plots_dir}/rgb.png'))
# terra::plotRGB(orig_rast, r = 54, g = 36, b = 20, 
#                scale = 10000,
#                stretch = 'lin', 
#                ext = my_ext, colNA = 'black')

# dev.off()
```

# Minerals and mixtures together

plot mineral level or mineral mixture levels together


## Group 2

### whole area
```{r}
mineral_agg <- glue('{tet_out_dir}/03_mineral_mix/group2um') %>% fs::dir_ls() %>% terra::rast()

mineral_agg_na <- terra::subst(mineral_agg, 0, NA)
em_mineral_max <- terra::app(mineral_agg_na, which.max, na.rm = TRUE)

plot(em_mineral_max, 
     colNA = 'white', 
    levels = names(mineral_agg),
     # ext = my_ext,
    axes = FALSE,
     type = 'class',
     main = glue('Group 2 Minerals and mixtures'),
    # col = my_grp2_pal2)
     col = c(scico::scico(n = 17, palette = 'vanimo', direction = 1)))
# dev.off()
```

### with zoom
```{r}
mineral_agg <- glue('{tet_out_dir}/03_mineral_mix/group2um') %>% fs::dir_ls() %>% terra::rast()
# plot(mineral_agg)
mineral_agg_crop <- crop_n_drop(mineral_agg, my_ext)

plot(mineral_agg_crop)

# plot(mineral_agg_crop_sub/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# mineral_agg_na <- terra::subst(mineral_agg, NA, 0) 
mineral_agg_na <- terra::subst(mineral_agg_crop, 0, NA)

# plot(mineral_agg_na/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# names(mineral_agg)
em_mineral_max <- terra::app(mineral_agg_na, which.max, na.rm = TRUE)



# pdf('{plots_dir}/group2_minsmix.pdf')
# plot(em_mineral_max, 
#      colNA = 'black', 
#      # ext = my_ext,
#      type = 'class',
#     axes = FALSE,
#     levels = names(mineral_agg_crop),
#      main = glue('Group 2 Minerals and mixtures'),
#      # col = sample(c(scico::scico(n = 17, palette = 'batlow', direction = -1))))
#     col = my_grp2_pal1)
# # dev.off()

# png('{plots_dir}/group2_minsmix.png')
# plot(em_mineral_max, 
#      colNA = 'black', 
#      ext = my_ext,
#     levels = names(mineral_agg_crop_sub),
#      type = 'class',
#      main = glue('Group 2 Minerals and mixtures'),
#      col = sample(c(scico::scico(n = 17, palette = 'batlow', direction = -1))))
# dev.off()
# png('{plots_dir}/group2_minerals2.png')

  plot(em_mineral_max, 
     colNA = 'black', 
    levels = names(mineral_agg_crop),
     ext = my_ext,
    axes = FALSE,
     type = 'class',
     main = glue('Group 2 Minerals and mixtures'),
    col = my_grp2_pal2)

p2 <- function(){
  plot(em_mineral_max, 
     colNA = 'black', 
    levels = names(mineral_agg_crop),
     ext = my_ext,
    axes = FALSE,
     type = 'class',
     main = glue('Group 2 Minerals and mixtures'),
    col = my_grp2_pal2)
}
     # col = c(scico::scico(n = 17, palette = 'vanimo', direction = -1)))
# dev.off()
```

## Group 1

### whole area
```{r}
mineral_agg <- glue('{tet_out_dir}/03_mineral_mix/group1um') %>% fs::dir_ls() %>% terra::rast()

mineral_agg_na <- terra::subst(mineral_agg, 0, NA)
em_mineral_max <- terra::app(mineral_agg_na, which.max, na.rm = TRUE)

plot(em_mineral_max, 
     colNA = 'white', 
    levels = names(mineral_agg),
     # ext = my_ext,
    axes = FALSE,
     type = 'class',
     main = glue('Group 1 Minerals and mixtures'),
    # col = my_grp2_pal2)
     col = c(scico::scico(n = 5, palette = 'lajolla', direction = -1)))
# dev.off()
```

```{r}
mineral_agg <- glue('{tet_out_dir}/03_mineral_mix/group1um') %>% fs::dir_ls() %>% terra::rast()

mineral_agg_crop <- crop_n_drop(mineral_agg, my_ext)
mineral_agg_na <- terra::subst(mineral_agg_crop, 0, NA)

# plot(mineral_agg_crop_sub)

# plot(mineral_agg_crop_sub/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# mineral_agg_na <- terra::subst(mineral_agg, NA, 0) 
# mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# names(mineral_agg)
em_mineral_max <- terra::app(mineral_agg_na, which.max, na.rm = TRUE)

# pdf('{plots_dir}/group1_minsmix.pdf')
plot(em_mineral_max, 
     colNA = 'black', 
     # ext = my_ext,
     type = 'class',
     axes = FALSE,
    levels = names(mineral_agg_crop),
     main = glue('Group 1 Minerals and mixtures'),
    col = my_grp1_pal)
     # col = sample(c(scico::scico(n = 4, palette = 'roma', direction = -1))))
# dev.off()

# png('{plots_dir}/group1_minsmix.png')
# plot(em_mineral_max, 
#      colNA = 'black', 
#      ext = my_ext,
#     levels = names(mineral_agg_crop),
#      type = 'class',
#      main = glue('Group 1 Minerals and mixtures'),
#      col = sample(c(scico::scico(n = 17, palette = 'batlow', direction = -1))))
# dev.off()
# png('{plots_dir}/group2_minerals2.png')
# plot(em_mineral_max, 
#      colNA = 'black', 
#     levels = names(mineral_agg_crop_sub),
#      ext = my_ext,
#     axes = FALSE,
#      type = 'class',
#      main = glue('Group 1 Minerals and mixtures'),
#      col = c(scico::scico(n = 17, palette = 'imola', direction = -1)))
# dev.off()
```

# Fit against grayscale background

```{r}
# group_id = 'group.1um'
# make_quickplots_zoom <- function(group_id, tet_out_dir, cube_path, my_out_dir, my_ext, ext_id = "area1"){
  # list all fit files in group
  fit_files <- fs::dir_ls(glue::glue('{tet_out_dir}/01_tetfits'), glob = '*.fit.gz', recurse = TRUE)
  # read into one stack
  my_rast <- terra::rast(fit_files)
  # replace 0 with NA to use for mask
  my_rast <- terra::subst(my_rast, 0, NA) 
  # read in original cube 
  orig_rast <- terra::rast(cube_path)
  # # set geometry to be able to mask
  # my_rast <- terra::set.crs(my_rast, orig_rast)
  # my_rast <- terra::set.ext(my_rast, orig_rast)
  # # pull one band for grayscale
  # future could do grayscale of rgb... 
  orig_bg <- orig_rast[[20]] # 552 nm pick a band for grayscale
  # stack background grayscale as many layers as in group
  bg_stack <- rep(orig_bg, nlyr(my_rast))
  # set names
  names(bg_stack) <- names(my_rast)
  # replace na with 0 because NAs are for detects
  orig_bg_subs <- terra::subst(bg_stack, NA, 0) 
  # mask as NA values in my_rast that are NOT NA
  orig_bg_mask <- terra::mask(orig_bg_subs, my_rast, maskvalues = NA, inverse = TRUE, updatevalue = NA)
  plot_dir <-  glue::glue('{plots_dir}/bg_fits')
  fs::dir_create(plot_dir)
  # for each layer save file 
  save_plot <- function(lyr_id){
    filename <- glue::glue('{plots_dir}/bg_fits/{names(my_rast)[lyr_id]}.pdf')
    pdf(filename)
    plot(orig_bg_mask[[lyr_id]], 
         col = scico::scico(100, palette = 'grayC'), 
         ext = my_ext,
         legend = FALSE, 
         axes = FALSE,
         main = gsub(pattern = '.fit', replacement = '', names(my_rast)[lyr_id]),
         colNA = 'red')
    dev.off()
  }
  purrr::walk(1:nlyr(my_rast), ~save_plot(lyr_id = .x))
  

```

# Minerals and mixtures


```{r}
mixtures_df <- readr::read_csv('Mixtures.csv')
# grp1_mixtures <- mixtures_df %>% dplyr::filter(group_name == 'group.1um') %>%  dplyr::pull(Dominant_Mineral) %>% unique()
# grp2_mixtures <- mixtures_df %>% dplyr::filter(group_name == 'group.2um') %>%  dplyr::pull(Dominant_Mineral) %>% unique()
# grp1_mixtures
# grp2_mixtures
```

plot minerals together for endmember

## Alunite

```{r}
my_mineral <- 'Alunite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group2um'
min_group_name <- 'group.2um'

mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     main = glue('{my_mineral} + minerals and mixtures fits'),
     col = colorspace::sequential_hcl(n = 255, palette = 'viridis'))
     # col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

plot(mineral_agg_na/255, 
     colNA = 'white', 
     ext = my_ext,
     main = glue('{my_mineral} + minerals and mixtures fits'),
     col = c('black', scico::scico(n = 255, palette = 'grayC', direction = 1))) 

# get endmembers for minerals and mixtures

mixture_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == my_mineral, group_name == min_group_name) %>% 
  dplyr::pull(tetracorder_file)
justmineral_ems <- minerals_df %>% 
  dplyr::filter(target == my_mineral, group_name == min_group_name) %>%
  dplyr::pull(tetracorder_file)
mineral_ems <- unique(c(justmineral_ems, mixture_ems))

em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_rast_na <- crop_n_drop(em_rast_na, my_ext)

em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

# pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_black.pdf'))
p3 <- function(){
  plot(em_mineral_max,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     colNA = 'black',
     levels = tools::file_path_sans_ext(names(em_rast_na)),
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
}
# dev.off()

# mineral_alpha <- mineral_agg/255
# mineral_alpha <- terra::subst(mineral_alpha, NA, 0)
# mineral_alpha <- crop_n_drop(mineral_alpha, my_ext)
# plot(mineral_alpha, ext = my_ext)
# em_mineral_max_nona <- terra::subst(em_mineral_max, NA, 999)
# 
# pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_walpha.pdf'))
# plot(em_mineral_max_nona,
#      alpha = mineral_alpha,
#      ext = my_ext, 
#      levels = c(names(em_rast_na), NA),
#      axes = FALSE,
#      type = 'classes',
#      # colNA = 'black',
#      main = glue("{my_mineral} minerals and mixtures"),
#      col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
# dev.off()

```

## Muscovite

```{r}
my_mineral <- 'Muscovite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group2um'
min_group_name <- 'group.2um'

mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'white', 
#      ext = my_ext,
#      main = glue('{my_mineral} + minerals and mixtures fits'),
#      col = c('black', scico::scico(n = 255, palette = 'grayC', direction = 1))) 

# get endmembers for minerals and mixtures

mixture_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == my_mineral, 
                group_name == min_group_name) %>% 
  dplyr::pull(tetracorder_file)

justmineral_ems <- minerals_df %>% 
  dplyr::filter(target == my_mineral, group_name == min_group_name) %>%
  dplyr::pull(tetracorder_file)
mineral_ems <- unique(c(justmineral_ems, mixture_ems))

em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_rast_na <- crop_n_drop(em_rast_na, my_ext)

em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

# pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_black.pdf'))
plot(em_mineral_max,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     colNA = 'black',
     levels = tools::file_path_sans_ext(names(em_rast_na)),
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
# dev.off()
```

## Kaolinite

```{r}
my_mineral <- 'Kaolinite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group2um'
min_group_name <- 'group.2um'

mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'white', 
#      ext = my_ext,
#      main = glue('{my_mineral} + minerals and mixtures fits'),
#      col = c('black', scico::scico(n = 255, palette = 'grayC', direction = 1))) 

# get endmembers for minerals and mixtures

mixture_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == my_mineral, 
                group_name == min_group_name) %>% 
  dplyr::pull(tetracorder_file)

justmineral_ems <- minerals_df %>% 
  dplyr::filter(target == my_mineral, group_name == min_group_name) %>%
  dplyr::pull(tetracorder_file)
mineral_ems <- unique(c(justmineral_ems, mixture_ems))

em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_rast_na <- crop_n_drop(em_rast_na, my_ext)

em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

# pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_black.pdf'))
plot(em_mineral_max,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     colNA = 'black',
     levels = tools::file_path_sans_ext(names(em_rast_na)),
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
# dev.off()
```

## any more? 

```{r}
my_mineral <- 'Montmorillonite'
# my_mineral <- 'Dickite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group2um'
min_group_name <- 'group.2um'

mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'white', 
#      ext = my_ext,
#      main = glue('{my_mineral} + minerals and mixtures fits'),
#      col = c('black', scico::scico(n = 255, palette = 'grayC', direction = 1))) 

# get endmembers for minerals and mixtures

mixture_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == my_mineral, 
                group_name == min_group_name) %>% 
  dplyr::pull(tetracorder_file)

justmineral_ems <- minerals_df %>% 
  dplyr::filter(target == my_mineral, group_name == min_group_name) %>%
  dplyr::pull(tetracorder_file)
mineral_ems <- unique(c(justmineral_ems, mixture_ems))

em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_rast_na <- crop_n_drop(em_rast_na, my_ext)

em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

# pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_black.pdf'))
plot(em_mineral_max,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     colNA = 'black',
     levels = tools::file_path_sans_ext(names(em_rast_na)),
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
# dev.off()
```

## Hematite

```{r}
my_mineral <- 'Hematite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group1um'
min_group_name <- 'group.1um'

mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'white', 
#      ext = my_ext,
#      main = glue('{my_mineral} + minerals and mixtures fits'),
#      col = c('black', scico::scico(n = 255, palette = 'grayC', direction = 1))) 

# get endmembers for minerals and mixtures

mixture_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == my_mineral, 
                group_name == min_group_name) %>% 
  dplyr::pull(tetracorder_file)

justmineral_ems <- minerals_df %>% 
  dplyr::filter(target == my_mineral, group_name == min_group_name) %>%
  dplyr::pull(tetracorder_file)
mineral_ems <- unique(c(justmineral_ems, mixture_ems))

em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_rast_na <- crop_n_drop(em_rast_na, my_ext)

em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

# pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_black.pdf'))
plot(em_mineral_max,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     colNA = 'black',
     levels = tools::file_path_sans_ext(names(em_rast_na)),
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
# dev.off()
```

## Georthite
```{r}
my_mineral <- 'Goethite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group1um'
min_group_name <- 'group.1um'

mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'white', 
#      ext = my_ext,
#      main = glue('{my_mineral} + minerals and mixtures fits'),
#      col = c('black', scico::scico(n = 255, palette = 'grayC', direction = 1))) 

# get endmembers for minerals and mixtures

mixture_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == my_mineral, 
                group_name == min_group_name) %>% 
  dplyr::pull(tetracorder_file)

justmineral_ems <- minerals_df %>% 
  dplyr::filter(target == my_mineral, group_name == min_group_name) %>%
  dplyr::pull(tetracorder_file)
mineral_ems <- unique(c(justmineral_ems, mixture_ems))

em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_rast_na <- crop_n_drop(em_rast_na, my_ext)

em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

# pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_black.pdf'))
plot(em_mineral_max,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     colNA = 'black',
     levels = tools::file_path_sans_ext(names(em_rast_na)),
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
# dev.off()
```
## non dominant group 2 mixtures

areal mixtures


```{r}
mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/group2um/group2_amix.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     main = glue('Group 2 Areal mixture fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

plot(mineral_agg_na/255, 
     colNA = 'white', 
     ext = my_ext,
     main = glue('Group 2 Areal mixture fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

mineral_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == 'none', MixtureType %in% c("Areal")) %>% 
  dplyr::pull(tetracorder_file)

em_fits <- glue('{tet_out_dir}/01_tetfits/group2um/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)

em_rast_crop <- terra::crop(em_rast, my_ext)

chk_vals <- function(rast_lyr_name){
  rast_lyr <- em_rast_crop[[rast_lyr_name]]
  max_val <- terra::values(rast_lyr) %>% unique() %>% max()
  max_val > 0
}

lyrs_to_keep <- purrr::map_lgl(names(em_rast), ~chk_vals(.x))

em_rast_crop_sub <- terra::subset(em_rast_crop, which(lyrs_to_keep))
em_rast_crop_sub_na <- terra::subst(em_rast_crop_sub, 0, NA)

plot(em_rast_crop_sub)

em_mineral_max <- terra::app(em_rast_crop_sub_na, which.max, na.rm = TRUE)

pdf(glue('atbd_plots/group2_amix_black.pdf'))
plot(em_mineral_max,
     # alpha = alunite_alpha,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     levels = tools::file_path_sans_ext(names(em_rast_crop_sub_na)),
     colNA = 'black',
     main = glue("Group2 Non dominant areal mixtures"),
     col = scico::scico(7, palette = 'imola', direction = -1))
dev.off()

mineral_alpha <- mineral_agg/255
plot(mineral_alpha, ext = my_ext)
em_mineral_max_nona <- terra::subst(em_mineral_max, NA, -999)

# # NOT CROPPED DOESNT WORK
# pdf(glue('atbd_plots/group2_amix_walpha.pdf'))
# plot(em_mineral_max_nona,
#      alpha = mineral_alpha,
#      ext = my_ext, 
#      type = 'classes',
#      # colNA = 'black',
#           # levels = names(em_rast_crop_sub_na),
#      main = glue("Group2_amix minerals"),
#      col = scico::scico(7, palette = 'imola', direction = -1))
# dev.off()

```

intimate mixtures

```{r}
mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/group2um/group2_imix.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     main = glue('Group 2 Intimate mixture fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

plot(mineral_agg_na/255, 
     colNA = 'white', 
     ext = my_ext,
     main = glue('Group 2 Intimate mixture fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

mineral_ems <- mixtures_df %>% 
  dplyr::filter(Dominant_Mineral == 'none', MixtureType %in% c("Intimate")) %>% 
  dplyr::pull(tetracorder_file)

em_fits <- glue('{tet_out_dir}/01_tetfits/group2um/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
plot(em_rast, ext = my_ext)

em_rast_crop <- terra::crop(em_rast, my_ext)

chk_vals <- function(rast_lyr_name){
  rast_lyr <- em_rast_crop[[rast_lyr_name]]
  max_val <- terra::values(rast_lyr) %>% unique() %>% max()
  max_val > 0
}

lyrs_to_keep <- purrr::map_lgl(names(em_rast), ~chk_vals(.x))

em_rast_crop_sub <- terra::subset(em_rast_crop, which(lyrs_to_keep))

em_rast_na <- terra::subst(em_rast, 0, NA)
em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

pdf(glue('atbd_plots/group2_imix_black.pdf'))
plot(em_mineral_max,
     # alpha = alunite_alpha,
     ext = my_ext, 
     type = 'classes',
     levels = names(em_rast_crop_sub),
     colNA = 'black',
     main = glue("Group2_imix minerals"),
     col = scico::scico(7, palette = 'imola', direction = -1))
dev.off()

mineral_alpha <- mineral_agg/255
plot(mineral_alpha, ext = my_ext)
em_mineral_max_nona <- terra::subst(em_mineral_max, NA, -999)

pdf(glue('atbd_plots/group2_imix_walpha.pdf'))
plot(em_mineral_max_nona,
     alpha = mineral_alpha,
     ext = my_ext, 
     type = 'classes',
     # colNA = 'black',
     main = glue("Group2_imix minerals"),
     col = scico::scico(7, palette = 'imola', direction = -1))
dev.off()

```


# Just minerals


## Group 2

## whole area

```{r}
mineral_agg2m <- glue('{tet_out_dir}/02_minerals_only/group2um') %>% fs::dir_ls() %>% terra::rast()
mineral_agg2m <- terra::subst(mineral_agg2m, 0, NA)

em_mineral_max2m <- terra::app(mineral_agg2m, which.max, na.rm = TRUE)

# pdf('{plots_dir}/group2_minsmix.pdf')
plot(em_mineral_max2m, 
     colNA = 'white', 
     # ext = my_ext,
     type = 'class',
    axes = FALSE,
    levels = names(mineral_agg2m),
     main = glue('Group 2 Minerals Only'),
     col = scico::scico(n = nlyr(mineral_agg2m), palette = 'batlow', direction = -1))
    # col = my_grp2_pal2)
# dev.off()
```


```{r}
mineral_agg <- glue('{tet_out_dir}/02_minerals_only/group2um') %>% fs::dir_ls() %>% terra::rast()
mineral_agg_crop <- crop_n_drop(mineral_agg, my_ext)
mineral_agg_crop <- terra::subst(mineral_agg_crop, 0, NA)
plot(mineral_agg_crop)

# plot(mineral_agg_crop_sub/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# mineral_agg_na <- terra::subst(mineral_agg, NA, 0) 
# mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# names(mineral_agg)
em_mineral_max <- terra::app(mineral_agg_crop, which.max, na.rm = TRUE)



# pdf('{plots_dir}/group2_minsmix.pdf')
plot(em_mineral_max, 
     colNA = 'black', 
     # ext = my_ext,
     type = 'class',
    axes = FALSE,
    levels = names(mineral_agg_crop),
     main = glue('Group 2 Minerals Only'),
     # col = sample(c(scico::scico(n = 17, palette = 'batlow', direction = -1))))
    col = my_grp2_pal2)
# dev.off()
```

## Group 1

```{r}
mineral_agg <- glue('{tet_out_dir}/02_minerals_only/group1um') %>% fs::dir_ls() %>% terra::rast()
mineral_agg_crop <- crop_n_drop(mineral_agg, my_ext)
mineral_agg_crop <- terra::subst(mineral_agg_crop, 0, NA)
plot(mineral_agg_crop)

# plot(mineral_agg_crop_sub/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# mineral_agg_na <- terra::subst(mineral_agg, NA, 0) 
# mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

# plot(mineral_agg_na/255, 
#      colNA = 'black', 
#      ext = my_ext,
#      col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# names(mineral_agg)
em_mineral_max <- terra::app(mineral_agg_crop, which.max, na.rm = TRUE)



# pdf('{plots_dir}/group2_minsmix.pdf')
plot(em_mineral_max, 
     colNA = 'black', 
     # ext = my_ext,
     type = 'class',
    axes = FALSE,
    levels = names(mineral_agg_crop),
     main = glue('Group 1 Minerals Only'),
     # col = sample(c(scico::scico(n = 17, palette = 'batlow', direction = -1))))
    col = my_grp1_pal)
# dev.off()
```


# Old below here

# Mineral level

```{r}
minerals_df <- readr::read_csv('Minerals.csv')
grp1_minerals <- minerals_df %>% dplyr::filter(group_name == 'group.1um') %>% dplyr::pull(target) %>% unique()
grp2_minerals <- minerals_df %>% dplyr::filter(group_name == 'group.2um') %>% dplyr::pull(target) %>% unique()
grp1_minerals
grp2_minerals
```

plot minerals together for endmember

```{r}
# my_mineral <- grp2_minerals[14]
# my_mineral_lwr <- stringr::str_to_lower(my_mineral)
# min_group <- 'group2um'

my_mineral <- 'Alunite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group2um'


mineral_agg <- terra::rast(glue('{tet_out_dir}/02_minerals_only/{min_group}/{my_mineral_lwr}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

mineral_agg_crop <- terra::crop(mineral_agg_na, my_ext)

chk_vals <- function(rast_lyr_name){
  rast_lyr <- mineral_agg_crop[[rast_lyr_name]]
  max_val <- terra::values(rast_lyr) %>% unique() %>% max()
  max_val > 0
}

lyrs_to_keep <- purrr::map_lgl(names(mineral_agg_crop), ~chk_vals(.x))

mineral_agg_crop_sub <- terra::subset(mineral_agg_crop, which(lyrs_to_keep))

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     main = glue('{my_mineral} fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', begin = 0, end = 1, direction = 1)))

plot(mineral_agg_na/255, 
     colNA = 'white', 
     ext = my_ext,
     main = glue('{my_mineral} fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

mineral_ems <- minerals_df %>% dplyr::filter(target == my_mineral) %>% dplyr::pull(tetracorder_file)
em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)

plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

pdf(glue('{plots_dir}/{my_mineral}_minerals_black.pdf'))
plot(em_mineral_max,
     # alpha = alunite_alpha,
     ext = my_ext, 
     levels = names(em_rast_na),
     axes = FALSE,
     type = 'classes',
     colNA = 'black',
     main = glue("{my_mineral} minerals"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
dev.off()

mineral_alpha <- mineral_agg_na/255
mineral_alpha <- terra::subst(mineral_alpha, NA, 0)
plot(mineral_alpha, ext = my_ext)

em_mineral_max_nona <- terra::subst(em_mineral_max, NA, 999)
# plot(em_mineral_max_nona, ext = my_ext, alpha = mineral_alpha)

pdf(glue('{plots_dir}/{my_mineral}_minerals_walpha.pdf'))
plot(em_mineral_max_nona,
     alpha = mineral_alpha,
     ext = my_ext, 
     levels = c(names(em_rast_na), NA),
     axes = FALSE,
     type = 'classes',
     # colNA = 'black',
     main = glue("{my_mineral} minerals"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
dev.off()

```

# Endmember level

Fit, depth, fd
Quantitative

```{r}
minerals_df <- readr::read_csv('Minerals.csv')
grp1_minerals <- minerals_df %>% dplyr::filter(group_name == 'group.1um') %>% dplyr::pull(target) %>% unique()
grp2_minerals <- minerals_df %>% dplyr::filter(group_name == 'group.2um') %>% dplyr::pull(target) %>% unique()
grp1_minerals
grp2_minerals
```

Plot fit for a mineral 

```{r}
# my_mineral <- grp2_minerals[14]
# my_mineral_lwr <- stringr::str_to_lower(my_mineral)
# min_group <- 'group2um'

my_mineral <- 'Alunite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group2um'


mineral_ems <- minerals_df %>% dplyr::filter(target == my_mineral) %>% dplyr::pull(tetracorder_file)
em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)

plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

pdf(glue('{plots_dir}/{my_mineral}_minerals_black.pdf'))
plot(em_mineral_max,
     # alpha = alunite_alpha,
     ext = my_ext, 
     levels = names(em_rast_na),
     axes = FALSE,
     type = 'classes',
     colNA = 'black',
     main = glue("{my_mineral} minerals"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
dev.off()

mineral_alpha <- mineral_agg_na/255
mineral_alpha <- terra::subst(mineral_alpha, NA, 0)
plot(mineral_alpha, ext = my_ext)

em_mineral_max_nona <- terra::subst(em_mineral_max, NA, 999)
# plot(em_mineral_max_nona, ext = my_ext, alpha = mineral_alpha)

pdf(glue('{plots_dir}/{my_mineral}_minerals_walpha.pdf'))
plot(em_mineral_max_nona,
     alpha = mineral_alpha,
     ext = my_ext, 
     levels = c(names(em_rast_na), NA),
     axes = FALSE,
     type = 'classes',
     # colNA = 'black',
     main = glue("{my_mineral} minerals"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
dev.off()

em_fit <- terra::rast(glue('{tet_out_dir}/01_tetfits/{min_group}/{my_mineral_lwr}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     main = glue('{my_mineral} fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', begin = 0, end = 1, direction = 1)))

plot(mineral_agg_na/255, 
     colNA = 'white', 
     ext = my_ext,
     main = glue('{my_mineral} fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 
```







# Minerals and mixtures


```{r}
mixtures_df <- readr::read_csv('Mixtures.csv')
# grp1_mixtures <- mixtures_df %>% dplyr::filter(group_name == 'group.1um') %>%  dplyr::pull(Dominant_Mineral) %>% unique()
# grp2_mixtures <- mixtures_df %>% dplyr::filter(group_name == 'group.2um') %>%  dplyr::pull(Dominant_Mineral) %>% unique()
# grp1_mixtures
# grp2_mixtures
```

plot minerals together for endmember

```{r}
my_mineral <- 'Alunite'
my_mineral_lwr <- stringr::str_to_lower(my_mineral)
min_group <- 'group2um'
```

```{r}
mineral_agg <- terra::rast(glue('{tet_out_dir}/03_mineral_mix/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     main = glue('{my_mineral} + minerals and mixtures fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

plot(mineral_agg_na/255, 
     colNA = 'white', 
     ext = my_ext,
     main = glue('{my_mineral} + minerals and mixtures fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

# get endmembers for minerals and mixtures
mixture_ems <- mixtures_df %>% dplyr::filter(Dominant_Mineral == my_mineral) %>% dplyr::pull(tetracorder_file)
justmineral_ems <- minerals_df %>% dplyr::filter(target == my_mineral) %>% dplyr::pull(tetracorder_file)
mineral_ems <- unique(c(justmineral_ems, mixture_ems))

em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
# plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_black.pdf'))
plot(em_mineral_max,
     ext = my_ext, 
     type = 'classes',
     axes = FALSE,
     colNA = 'black',
     levels = names(em_rast_na),
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
dev.off()

mineral_alpha <- mineral_agg/255
mineral_alpha <- terra::subst(mineral_alpha, NA, 0)
plot(mineral_alpha, ext = my_ext)
em_mineral_max_nona <- terra::subst(em_mineral_max, NA, 999)

pdf(glue('{plots_dir}/{my_mineral}_mineralsMIX_walpha.pdf'))
plot(em_mineral_max_nona,
     alpha = mineral_alpha,
     ext = my_ext, 
     levels = c(names(em_rast_na), NA),
     axes = FALSE,
     type = 'classes',
     # colNA = 'black',
     main = glue("{my_mineral} minerals and mixtures"),
     col = scico::scico(nlyr(em_rast_na), palette = 'imola', direction = -1))
dev.off()

```



# Mineral group

plot mineral level or mineral mixture levels together

```{r}
mineral_agg <- glue('{tet_out_dir}/02_minerals_only/group2um') %>% fs::dir_ls() %>% terra::rast()
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

names(mineral_agg_na)
em_mineral_max <- terra::app(mineral_agg_na, which.max, na.rm = TRUE)

pdf('{plots_dir}/group2_minerals.pdf')
plot(em_mineral_max, 
     colNA = 'black',
     ext = my_ext,
     levels = names(mineral_agg_na),
     type = 'class',
     main = glue('Group 2 Minerals'),
     col = sample(c(scico::scico(n = 17, palette = 'batlow', direction = -1))))
dev.off()

png('{plots_dir}/group2_minerals.png')
plot(em_mineral_max, 
     colNA = 'black', 
     ext = my_ext,
      levels = names(mineral_agg_na),
     type = 'class',
     main = glue('Group 2 Minerals'),
     col = sample(c(scico::scico(n = 17, palette = 'batlow', direction = -1))))
dev.off()

png('{plots_dir}/group2_minerals2.png')
plot(em_mineral_max, 
     # colNA = 'white', 
     colNA = 'black', 
     ext = my_ext,
     levels = names(mineral_agg_na),
     type = 'class',
     main = glue('Group 2 Minerals'),
     col = sample(c(scico::scico(n = 17, palette = 'vanimo', direction = -1))))
dev.off()
```

```{r}
mineral_agg <- glue('{tet_out_dir}/02_minerals_only/group1um') %>% fs::dir_ls() %>% terra::rast()
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

summary(mineral_agg_na$epidote)
names(mineral_agg)
em_mineral_max <- terra::app(mineral_agg_na, which.max, na.rm = TRUE)
# which.max cant handle all na?
# NOT PLOTTING CORRECTLY
# png('{plots_dir}/group1_minerals.png')
# plot(em_mineral_max,
#      colNA = 'black',
#      ext = my_ext,
#      type = 'class',
#      levels = names(mineral_agg),
#      axes = FALSE,
#      main = glue('Group 1 Minerals'),
#      col = c(scico::scico(n = nlyr(mineral_agg), palette = 'hawaii', direction = 1)))
# dev.off()

# png('{plots_dir}/group1_minerals2.png')
plot(em_mineral_max, 
     colNA = 'black', 
     ext = my_ext,
     type = 'class',
     levels = names(mineral_agg),
     axes = FALSE,
     main = glue('Group 1 Minerals'),
     col = c(scico::scico(nlyr(mineral_agg), palette = 'roma', direction = 1)))
# dev.off()
```



# All endmembers for a group

(showing that there is overlap in pixels)


```{r}
allems_df <- readr::read_csv('MineralsAll.csv')
```

plot minerals together for endmember

```{r}
my_mineral <- 'alunite'
my_mineral_cap <- stringr::str_to_title(my_mineral)
min_group <- 'group2um'
```

```{r}
mineral_agg <- terra::rast(glue('{tet_out_dir}/04_minerals_all/{min_group}/{my_mineral}.tif'))
mineral_agg_na <- terra::subst(mineral_agg, 0, NA) 

plot(mineral_agg_na/255, 
     colNA = 'black', 
     ext = my_ext,
     main = glue('{my_mineral} + {my_mineral} mixtures fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

plot(mineral_agg_na/255, 
     colNA = 'white', 
     ext = my_ext,
     main = glue('{my_mineral} + {my_mineral} mixtures fits'),
     col = c('black', scico::scico(n = 255, palette = 'imola', direction = 1))) 

mineral_ems <- allems_df %>% dplyr::filter(target == my_mineral_cap) %>% dplyr::pull(tetracorder_file)
em_fits <- glue('{tet_out_dir}/01_tetfits/{min_group}/{mineral_ems}.fit.gz')
em_rast <- terra::rast(em_fits)
plot(em_rast, ext = my_ext)
em_rast_na <- terra::subst(em_rast, 0, NA)
em_mineral_max <- terra::app(em_rast_na, which.max, na.rm = TRUE)

pdf(glue('atbd_plots/{my_mineral}_mineralsALL_black.pdf'))
plot(em_mineral_max,
     # alpha = alunite_alpha,
     ext = my_ext, 
     levels = names(em_rast_na),
     type = 'classes',
     colNA = 'black',
     main = glue("{my_mineral_cap} all EMs"),
     col = scico::scico(7, palette = 'imola', direction = -1))
dev.off()

mineral_alpha <- mineral_agg/255
plot(mineral_alpha, ext = my_ext)
em_mineral_max_nona <- terra::subst(em_mineral_max, NA, -999)

pdf(glue('atbd_plots/{my_mineral}_mineralsALL_walpha.pdf'))
plot(em_mineral_max_nona,
     alpha = mineral_alpha,
     ext = my_ext, 
     type = 'classes',
     # colNA = 'black',
     main = glue("{my_mineral_cap} all EMs"),
     col = scico::scico(7, palette = 'imola', direction = -1))
dev.off()

```